---
title: "Exploratorio_Walmart"
author: "Santiago"
date: "11/28/2020"
output: html_document
---


#Cargar funcione de UTILS 


```{r}




```



## Exploratorio Walmart

```{r}
#Cargamos paquetes 

library(tidyverse)

library(readr)


library(ggthemes)

```


## Cargamos los datos 

```{r setup }




walmart<-load_train()

 
```

 

```{r cars}
glimpse(walmart)
```


Información sobre las columnas:

Data fields
TripType - a categorical id representing the type of shopping trip the customer made. This is the ground truth that you are predicting. TripType_999 is an "other" category.
VisitNumber - an id corresponding to a single trip by a single customer
Weekday - the weekday of the trip
Upc - the UPC number of the product purchased
ScanCount - the number of the given item that was purchased. A negative value indicates a product return.
DepartmentDescription - a high-level description of the item's department
FinelineNumber - a more refined category for each of the products, created by Walmart



```{r pressure }
 head(walmart)
```
 
 
 
 ### Analisis univariado (pendiente)
 

 
 
 # Análisis Bivariado


 Correlación de las columnas con la variable de salida: 
 
 Empezamos haciendo un análisis de correlación entre las variables numéricas.
En particular, nos interesa destacar las variables que tienen una alta correlacion positiva o negativa, con la variable price, que es la variable a predecir. 
 
 
```{r}

#Las variables numericas
walmart_numeric<-walmart %>% select(where(is.numeric))

## Correlacion entre variables numericas 
cor_matrix<-round(cor(walmart_numeric, use="complete.obs" ),2)

melted_walmart <- melt(cor_matrix)

heat_cor_numeric_walmart<-ggplot(data = melted_walmart, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()+
  theme(axis.text.x = element_text(angle=90))

heat_cor_numeric_walmart

```
 
```{r}

```

